%! Author = Aniruddha
%! Date = 4/18/2025

% Preamble
\documentclass[11pt]{resume}

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Aniruddha Nath} % Your name
% You can merge both of these into a single line if you do not have a website.
\address{+91-801-367-0017 \\ Bengaluru, KA, IN}
\address{\href{mailto:aniruddha.nath.work@gmail.com}{aniruddha.nath.work@gmail.com} \\ \href{https://www.linkedin.com/in/aniruddha-nath/}{LinkedIn} \\ \href{www.faangpath.com}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

    \begin{rSection}{OBJECTIVE}

    {Experienced Senior Software Engineer with over 6 years of expertise in conceptualizing, developing, and validating intricate systems. Currently focused on .NET Development, with a strong command of C Sharp, Dot NET Core, ASP.NET MVC, including HTML, CSS, and JavaScript (jQuery and Angular). Beyond Dot Net, I am proficient in Salesforce Cloud Platform and related technologies. Committed to applying a resourceful skill set to deliver creative solutions and surpass organizational goals.}


    \end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

    \begin{rSection}{Education}

    {\bf Bachelor of Technology} | Swami Vivekanand University \hfill {July 2013 - June 2017}\\
    \textbf{Major:} Computer Science and Engineering | CGPA: 6.9

        {\bf Higher Secondary} | West Bengal Council of Higher Secondary Education \hfill {July 2011 - June 2013}\\
    \textbf{Major:} Science | Bandel St. John's High School | 58.4%

        {\bf Secondary} | West Bengal Board of Secondary Education \hfill {July 2009 - June 2011}\\
    \textbf{Major:} General Studies | Hooghly Branch Govt. High School | 73.6%

%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


    \end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS
%----------------------------------------------------------------------------------------
    \begin{rSection}{SKILLS}

        \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
            \textbf{Technical Expertise:}\\\\
            \textbf{Database} & MS SQL, Oracle, MySQL.\\
            \textbf{Programming Language} & C Sharp, Apex.\\
            \textbf{Frameworks} &   Salesforce Lightning Development Framework,  Dot NET Framework 4.7,\\
            &   Dot NET Core 3.1, Dot NET 8.\\
            \textbf{Front-end} &    HTML, JavaScript, jQuery 3.3+, Angular 6+.\\
            \textbf{Cloud} &    Salesforce Development Cloud (SFDC), Salesforce Health Cloud (SFHC).\\
            \textbf{IDE} &  Visual Studio 2017, 2019, 2022, MS SQL Server 2014, 2016, 2019, IntelliJ IDEA 2024.1\\
            \\\\
            \textbf{Areas of Expertise:}    &    Adaptable.\\
            &    Teamwork and Collaboration.\\
            &    Conflict Management.\\
            &    Decision making.\\
            &    Efficient Task Management.\\
            &    Adaptability.\\
        \end{tabular}\\
    \end{rSection}

    \begin{rSection}{EXPERIENCE}

        \textbf{Senior Software Engineer} \hfill August 2023 - Present\\
        Ecolab Digital Center \hfill \textit{Bengaluru, KA, IN}
        \begin{itemize}
            \itemsep -3pt {}
            \item Led a groundbreaking digital transformation endeavor at Ecolab Digital Solutions, harnessing .NET technologies alongside Salesforce Platform to revolutionize operations; enhanced customer experience, resulting in a 30\% increase in customer retention and a 25\% boost in cross-selling opportunities.
            \item Coordinated the thorough collection and analysis of requirements provided by the product team, leveraging user data and market research to inform strategic decision-making.
            \item Led the coordination of Apex, Aura, and Lightning Web Components in development projects.
            \item Architected and implemented a cutting-edge solution for integrating Salesforce Platform APIs with .NET-based web applications.
            \item Collaborated with the migration team on migrating the web API based on .NET Core 3.1 to .NET 7.
            \item Executed the implementation of Azure DevOps to streamline version control and effectively manage 200+ product backlog items, ensuring seamless alignment with project specifications and accelerating development timelines by 40\%.
        \end{itemize} \hfill \newline

        \textbf{Developer Support Engineer} \hfill April 2022 - August 2023\\
        Salesforce India Pvt. Ltd. \hfill \textit{Hyderabad, TS, IN}
        \begin{itemize}
            \itemsep -3pt {}
            \item Spearheaded script activities with AMPScript and SSJS in Marketing Cloud Business Units to enhance email personalization and performance, resulting in a 50\% decrease in unsubscribe rates and a 20\% increase in customer retention.
            \item Implemented a proactive approach in troubleshooting CloudPages issues, reducing resolution time by 40\% and improving client satisfaction by 25\% through personalized support strategies.
            \item Constructed personalized CloudPages for clients using AMPScript and SSJS methodologies; drove a 35\% increase in click-through rates and a 15\% boost in overall customer satisfaction scores.
            \item Piloted a sophisticated data integration initiative connecting Sales Cloud and Marketing Cloud, which catalyzed a 20\% increase in sales pipeline velocity and a 15\% enhancement in customer engagement metrics.
            \item Engineered a comprehensive GitHub workflow for version control and requirements analysis, leading to a 35\% increase in development efficiency and a 20\% reduction in code conflicts.
        \end{itemize} \hfill \newline

        \textbf{Software Developer} \hfill February 2019 - April 2022\\
        Cyber Swift Infotech Pvt. Ltd. \hfill \textit{Kolkata, WB, IN}
        \begin{itemize}
            \itemsep -3pt {}
            \item Spearheaded the development of a robust care management system for P3 Health Partners, USA, and CleverCare Health Partners, USA, utilizing Salesforce CRM in conjunction with Health Cloud and Dot NET based CRM.
            \item Drove client engagement initiatives, ensuring project milestones were met; streamlined project delivery process and reduced project delivery time by an average of 20\%, resulting in a 10\% increase in client referrals.
            \item Architected applications to exact specifications utilizing Apex Controllers, Batches, Triggers, and the Lightning Framework, incorporating Aura and LWC components; streamlined processes, reducing project timelines by 30\%.
            \item Engineered and executed strategic partnerships with PDFButler, Avaya Telephony System, and Cisco Telephony, resulting in a 40\% decrease in call handling time and a 25\% increase in customer satisfaction rates.
            \item Engineered the adoption of Talend Open Studio ETL Tools for data migration, optimizing data processing speed by 50\% and reducing manual data transfer errors by 75\%, resulting in enhanced data integrity.
            \item Optimized Salesforce Orgs Deployment processes by implementing Change Sets, Workbench, and ClickDeploy from Copado, resulting in a 40\% reduction in deployment time and a 30\% increase in successful deployments.
            \item Orchestrated the optimization of version control processes by integrating BitBucket and JIRA, leading to a 30\% reduction in development cycle time and a 15\% increase in bug resolution efficiency.
            \item Architected a GIS Survey Application based on .NET Core 3.1 and Angular 7, facilitating streamlined data collection and analysis.
            \item Managed user access for the Survey Admin portal, ensuring adherence to project requirements and data security best practices; implemented role-based access controls, enhancing data confidentiality and reducing security breaches.
            \item Conducted regular client and user monitoring activities weekly to ensure operational efficiency.
            \item Contributed to developing an internal HRMS application based on .NET MVC and Angular 7, focusing on building Leave and Profit-Loss modules.
            \item Orchestrated comprehensive version control management with GitLab, facilitating seamless collaboration among cross-functional teams and achieving a 15\% improvement in product delivery timelines.
        \end{itemize} \hfill \newline

        \textbf{Junior Software Engineer} \hfill December 2018 - January 2019\\
        ZINFI Software Systems Pvt. Ltd. \hfill \textit{Kolkata, WB, IN}
        \begin{itemize}
            \itemsep -3pt {}
            \item Enhanced UCM product functionality by implementing strategic adjustments with MS SQL Server; optimized data retrieval operations, leading to a 30\% reduction in server response time and a 15\% boost in system efficiency.
        \end{itemize} \hfill \newline

    \end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

    \begin{rSection}{PROJECTS}
        \vspace{-1.25em}
        \item \textbf{Ecolab Sales and Service} | {The Ecolab Sales and Service (ESS) app facilitates seamless communication between Ecolab's Field Representatives and Customers, enabling direct engagement with the company's offerings.} \newline
        \textbf{Tech Stacks} | {Sales Cloud, Health Cloud, Dot NET 8}

        \item \textbf{Marketing Cloud Journey Builder, CloudPages, Automation Studio, and Marketing Cloud Connector} | {Marketing Cloud Journey Builder and Automation Studio empower users to automate customer marketing journeys seamlessly. From initiating email campaigns to orchestrating comprehensive marketing initiatives, these tools leverage Salesforce Marketing Cloud Journeys and Activities to streamline operations. CloudPages functionality enables clients to develop custom scripts using AMPScript and SSJS, facilitating the creation and synchronization of records between Salesforce Marketing Cloud and Sales Cloud.} \newline
        \textbf{Tech Stacks} | {Sales Cloud, Marketing Cloud, AMPScript, SSJS, MS SQL}

        \item \textbf{P3 Healthcare Systems and CleverCare Healthcare Solutions} | {P3 Healthcare Solutions and CleverCare Healthcare Solutions, leading healthcare providers in the US, underwent a transformative shift with the implementation of Salesforce Health, Sales, and Service Clouds. This migration facilitated a seamless transition from outdated legacy systems to modern healthcare infrastructure. Furthermore, the integration upgraded existing care plan processes, ensuring enhanced efficiency and effectiveness in service delivery.} \newline
        \textbf{Tech Stacks} | {Sales Cloud, Health Cloud, Apex, Aura, Lightning Web Component, Visualforce, Flows, Dot Net Core 3.1, Dot Net Web API, Dot Net MVC}

        \item \textbf{GIS Survey App} | {The GIS Survey Web App, constructed on Dot NET Core 3.1, efficiently handles requests originating from its native mobile companion via the Dot NET Core Web API. Furthermore, the Survey Admin section is a centralized platform for comprehensive reporting and analysis of survey data.} \newline
        \textbf{Tech Stacks} | {Angular 7, Dot Net Framework 4.5, Dot Net Core 3.1, C Sharp and MS SQL Server}

        \item \textbf{Unified Channel Management (UCM)} | {UCM streamlines sales operations for ZINFI channel partners, facilitating product transactions through CRM integration. For instance, channel partners like HP can leverage UCM to distribute their products to retailers efficiently, simplifying the sales process.} \newline
        \textbf{Tech Stacks} | {C Sharp and MS SQL Server}
    \end{rSection}

%----------------------------------------------------------------------------------------
    \begin{rSection}{Certifications}
        \begin{itemize}
            \item   Salesforce Certified Administrator.
            \item   Salesforce Certified Platform Developer I.
            \item   Salesforce Certified Marketing Cloud Email Specialist.
            \item   Salesforce Certified Marketing Cloud Administrator.
        \end{itemize}
    \end{rSection}
\end{document}
